---
title: "FirstBeamerPrez"
author: "LaurenBomeisl"
date: "1/30/2018"
output: 
  beamer_presentation: 
    colortheme: beaver
    incremental: yes
    theme: Madrid
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Slide Title

Add your markdown text

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## First Slide

- First Incremental bullet point
- Second
- Third

## Third Slide

>-first simultaneous bullet point
>-second simultaneous bullet point
>-third simultaneous bullet point

% comment

##Let's see some R

```{r, echo=FALSE}
library(ggplot2)
var1 <- runif(10)
var2 <- runif(10)
qplot(x=var1, y=var2)
```

##Colored bullet points
>- collection mode
>- \color{gray} Spatial and Temporal
>- \color{red} Taxonomic Bias
>- \color{gray} Sampling \color{black}
>- more stuff

##Pulling in images


 \begin{picture}(320,250)
 \put(85,75){\includegraphics[height=6cm]
 {celtic.jpg}}
 \put(00,60){\begin{minipage}[t]{1\linewidth}
 {Choose a point on the unit circle. Connect it to 
 the origin with a line of 
 length one, and denote the angle between that line 
 and the horizontal 
 coordinate axis by $\theta$.}
 \end{minipage}}
 \end{picture}
 
 



## Slide with Plot
