---
title: "ElevatrPresentation"
author: "LaurenBomeisl"
date: "5/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Start with Preliminaries
```{r echo=T, warning=FALSE}
  library(elevatr)  # for elevation inqueries
  library(sp)  # for spatial dataset classification
  library(rgdal)  # for transformation
  library(raster)  # for raster plotting
  library(lattice)  # for contour plotting
  library(rasterVis)  # also for contour plotting
```

#### Identify application programming interface for raster creation

```{r}
set_api_key("https://aws.amazon.com/public-datasets/terrain/")
```


#### To begin, choose your own adventure!

```{r}
  #northwest coordinates
  maxlat<- 47.7
  minlong<- -121.1
  #southeast coordinates
  minlat<- 47.3
  maxlong<- -120.5
  
  #determine time zone for transformation
  epsg<-"+init=EPSG:4410"
```


#### Why is the time zone (epsg code) important? Projection required to identify gravitational threshold//sea level

```{r}

  # set seed for reproducible results
  set.seed(76)
  # set number of iterations (the higher the greater resolution)
  n<- 200

```


#### Creating your spatial dataset from scratch

```{r}
  spCoord <- SpatialPoints(data.frame(
    x = runif(n, min = minlong, max = maxlong), 
    y = runif(n, min = minlat, max = maxlat)),
    proj4string = CRS("+proj=longlat"))
  summary(spCoord) # notice projection = false

```


#### Transform coordinate system

```{r}
  # Set Coordinate Reference System using the epsg code, based UTM zone
  sp <-spTransform(spCoord,CRS(epsg))
  summary(sp)    # notice projection now = true
```


#### If read in file from csv, how can projection be checked?

```{r}
  is.projected(sp) # check to make sure the data frame was projected
  proj4string(sp)  #query CRS projection
  projection(sp)
```


#### Compare geographic vs. projected coordinate system

```{r}
  plot(spCoord, axes=TRUE)
  plot(sp, axes=TRUE)
```


#### Now let's set up a spatial dataframe to access elevation data

```{r}
  spdf<-SpatialPointsDataFrame(sp, data.frame(sp),
                         proj4string=proj4string(sp),
                         bbox = NULL)
    summary(spdf)
    # now our dataset is in a format that can be used to query elevation
    elev<-get_elev_point(spdf,
                       prj = proj4string(spdf),
                       src = "epqs")
    #note: defaults to mapzen, but as of this past January this source is no longer an option, thus we will use the Elevation Point Query Service (epqs)
```


#### Tripple check projection, check for NA elevation values,
and illustrate your Raster!

```{r}
  # tripple check projection
  is.projected(elev)
  # ensure there are no NA elevation values from query
  !is.na(elev$elevation)
  summary(elev)
  
    raster<-get_elev_raster(spdf,elev$elevation, 
                            prj = proj4string(elev), 
                            src = "aws",
             set_api_key("https://aws.amazon.com/public-datasets/terrain/"),
                  z=5)   
    
  plot(raster)
  # Once you can see what you're doing, play with the zoom!
  
  # we can also choose a specific range to observe
  image(raster, xlim=c(2000000,4000000),main="Zoomed In")
  
  # Or we can select a unique z values to observe
  image(raster, zlim=c(1500,2000),col=terrain.colors(5))  
    
  # Alternatively, we can look at the distribution of z values within the raster
    hist(raster, main="Distribution of Elevation Values", 
       col= "purple", 
       maxpixels=10000)
```


### Now that we have a projected raster, we can also play with lattice

```{r}
  contour<-contour(raster,nlevels=8)

  #Play with the nlevels to your desired detail
  
  contourplot(raster,labels=FALSE)
  
```


#### We can also evaluate geographic/terrain characteristics

```{r}
  # What is the minimum or maximum slope in this grid?
  terrain(raster,opt = 'slope')
    # terrain() can also be used to observe aspect ratio, and flow direction
    # or to evaluate resolution via the terrain ruggedness index,
    # topographic position index, roughness, and flow direction
  
    # query coordinate for maximum elevation
    maxpointx<-elev$x[which.max(elev$elevation)]
    maxpointy<-elev$y[which.max(elev$elevation)]


    # Determine flowpath from highest point
    # create flow direction output to pass through flowpath
    #flowdir<- terrain(raster,opt='flowdir')
    #print(flowdir)
  
    #Identify cell with max elevation to pass through flowPath
    # cell<-cellFromRow(elev,which.max(elev$elevation))
  
    # pass flow direction output and max elevation coordinate through flowPath
    # flowPath(flowdir,cell)
```


